Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-06 manuscript.tex
Add files via upload
went through the paper, slightly updated Xavier's comments.

%We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion. Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically. %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}. We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet. 
The proposed model from Eq.~\ref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table \ref{table:spotplanet.test}.   Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet. 
\xavier{We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are comparable in terms of rms for all the three different RV estimates, with SN mean RV giving a slightly smaller value.}
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
%   \caption{Set of  variations in RVs estimated using a Normal and a SN fit before and once corrected from stellar activity. In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet. The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}. In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RVs caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
%    \label{fig:spotplanet.correction}
%\end{figure*}

@@

The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs derived estimated using the SN density and the Normal density. 
The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar. 
This behavior is similar to the faculae simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B. \xavier{Another argument in favour of the faculae, is the presence of the positive correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV seen in Fig.~\ref{fig:alphacent:corrPlot}. In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV and no correlation between SN FWHM and SN mean RV}.
\citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting. This happens because the mean of the SN is more sensitive to stellar activity. In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity. On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean. The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect. Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
%   \caption{(top) RVs as function of Julian Day for Alpha Centauri B. The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses). (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
%   \label{fig:alphacent:diff:RV}
%\end{figure*}
%

Similar to the analyses in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}. 
For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN. 
\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
\xavier{I create a new subsection after this one to discuss rapidly th eother stars}
\xavier{It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest. 
The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
When looking at the correlation between the width and the RV estimate for Alpha Cen B, once again the correlation is the strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, while it is equals to $R=0.7$ for the correlation between FWHM and N mean RV.}
%
%The correlations between $\gamma$ and SN mean RV, and also SN FWHM and SN mean RV
%
%Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs. In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV. The correlation between FWHM and the RVs, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN density rather than a Normal. All the correlations are statistically different from $0$. Recalling the analyses presented in Sec. \ref{sec:soap}, we could infer that Alpha Centauri B is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
%%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
   \caption{Correlations between the asymmetry parameters and their corresponding RVs for Alpha Centauri B. The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits. The correlations are always stronger when using parameters derived from the SN fit than the Normal one. The p--values associated with each $R$ is statistically different from $0$.} 
   \label{fig:alphacent:corrPlot}
\end{center}
\end{figure*}
%

The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
For Alpha Cen B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
the remaining RV rms of the residuals are essentially the same for all three approaches.
%In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
\xavier{Although, when studying the correlations between the different parameters, we see that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density,
the proposed linear model for correcting stellar activity is not able to perform better in the SN case than in the Normal case.}
\xavier{@Jessi: I deleted "after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal" as it was giving the wrong impression that the SN parameters are useless}
\xavier{Comparing the new correction proposed in Sec.~\ref{sec:31} to correct for activity and the usual correction only using a linear combination of the width and the asymmetry of the CCF, we see very similar efficiency. The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.}
%it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
%we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.

@@

\xavier{The preceding section was analysing the improvement brought by the SN parameters compared to the Nomral parameters and the BIS SPAN. Here we do a similar analysis for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7. The same correlation plots, and activity-correction plots that was found in the preceding section can be found found for those new stars in Appendix \ref{appendix}.

When looking to the correlation between the parameters, we arrive to the same conclusions than for Alpha Cen B. The correlation between $\gamma$ and SN mean RV is always the strongest among all the other asymmetry-RV corrleations not derived with SN parameters. For the correlation between the width and the RV, the strongest correlation is also found for all the stars between SN FWHM and SN mean RV. There is one exception however, in the case of HD10700, the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is only $R=0.42$ for the correlation between SN FWHM and SN mean RV.

Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything. This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).

In terms of activity correction, we see like in the case of Alpha Cen B, that although the RV rms is larger when measuring the RVs using SN mean RV compared to the RVs derived using N mean RV, after correcting for activity using the new model proposed in Sec.~\ref{sec:31}, both RV estimates gives similar residuals. We also see nearly no significant differences between the new correction proposed and the usual correction only using a linear combination of the width and the asymmetry of the CCF. There is only in the case of Corot-7 where the new correction is able to get a RV residual rms 30\,\cms smaller than the usual correction.}

@@

%HD10700
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}10700$. The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits. The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one. \umberto{The correlation between the FWHM and the RVs is, only for this quiet star, stronger when using the parameter retrieved with the Normal distribution}. The p--values associated with each $R$ are statistically different from $0$, except for the correlation between FIG BIS- and RV (p--values=0.36).}   
   \label{fig:Tau:corrPlot}
\end{center}
\end{figure*}

>>>>

%We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion. Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically. %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}. We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet. 
The proposed model from Eq.~\ref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table \ref{table:spotplanet.test}.   Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet. We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are comparable in terms of rms for all the three different RV estimates, with SN mean RV giving a slightly smaller value.
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
%   \caption{Set of  variations in RVs estimated using a Normal and a SN fit before and once corrected from stellar activity. In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet. The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}. In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RVs caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
%    \label{fig:spotplanet.correction}
%\end{figure*}

@@

The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs derived estimated using the SN density and the Normal density. 
The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar. 
This behavior is similar to the faculae simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B. \umberto{Another argument that suggests the presence of faculae, is the strong positive measured correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}. In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV, while weak correlations are measured between SN FWHM and SN mean RV}.
\citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting. This happens because the mean of the SN is more sensitive to stellar activity. In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity. On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean. The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect. Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
%   \caption{(top) RVs as function of Julian Day for Alpha Centauri B. The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses). (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
%   \label{fig:alphacent:diff:RV}
%\end{figure*}
%

Similar to the analyses in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}. 
For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN. 
\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
\xavier{I create a new subsection after this one to discuss rapidly th eother stars}
\umberto{It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest. 
The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
When looking at the correlations between the width and the RV estimates for Alpha Cen B, once again the correlation is strongest for the parameters retrieved form the SN density, with $R=0.82$ for SN FWHM-SN mean RV, while it is equals to $R=0.7$ for the correlation between FWHM and N mean RV.}
%
%The correlations between $\gamma$ and SN mean RV, and also SN FWHM and SN mean RV
%
%Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs. In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV. The correlation between FWHM and the RVs, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN density rather than a Normal. All the correlations are statistically different from $0$. Recalling the analyses presented in Sec. \ref{sec:soap}, we could infer that Alpha Centauri B is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
%%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
   \caption{Correlations between the asymmetry parameters and their corresponding RVs for Alpha Centauri B. The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits. The correlations are always stronger when using parameters derived from the SN fit than the Normal one. The p--values associated with each $R$ is statistically different from $0$.} 
   \label{fig:alphacent:corrPlot}
\end{center}
\end{figure*}
%

The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
For Alpha Cen B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
the remaining RV rms of the residuals are essentially the same for all three approaches.
%In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
\umberto{Although when studying the correlations between the different parameters we see that the parameters retrieved by using the SN density are more sensitive to stellar activity than the ones obtained with a Normal density fit,
the proposed linear model for correcting from stellar activity is not able to perform better in the SN case than in the Normal case.}
\xavier{@Jessi: I deleted "after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal" as it was giving the wrong impression that the SN parameters are useless}
\umberto{When comparing the new correction for stellar activity proposed in Sec.~\ref{sec:31} with the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF, we end up with very similar results. The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.}
%it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
%we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.

@@

\umberto{In the previous section we evaluated the improvement obtained by the SN parameters respect to the Normal parameters and the BIS SPAN. We execute similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7. The same correlations plots and activity--after--correction plots displayed in the previous section for Alpha Cen B can be found found for those new four stars in Appendix \ref{appendix}.

When looking to the correlation between the parameters, we arrive to the same conclusions obtained for Alpha Cen B. The correlation between $\gamma$ and SN mean RV is always the strongest among all the asymmetry-RV correlations not retrieved by the SN parameters. For the correlation between the width and the RV, the strongest correlation is also found for all the stars between SN FWHM and SN mean RV. There is one exception however, in the case of HD10700: the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is only $R=0.42$ for the correlation between SN FWHM and SN mean RV.

Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything. This is the case for the evaluation of the asymmetry-RV correlations for HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).

In terms of correction for stellar activity, in the case of Alpha Cen B we see that although the RV rms is larger when measuring the RVs using SN mean RV (respect to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates provides similar residuals. We also observe slight differences in the rms between the new proposed correction and the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF. Only in the case of Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.}

@@

%HD10700
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}10700$. The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits. The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one. The correlation between the FWHM and the RVs is, only for this quiet star, stronger when using the parameter retrieved with the Normal distribution. The p--values associated with each $R$ are statistically different from $0$, except for the correlation between FIG BIS- and RV (p--values=0.36).}   
   \label{fig:Tau:corrPlot}
\end{center}
\end{figure*}
